Behavior Driven Development in Haskell

### 2012-06-01 paper.tex
Update comment
Update comments

\begin{quote}
    TBD: Section -> section
\end{quote}

@@

\begin{quote}
    TBD: introduce \emph{test driver}
\end{quote}

@@

@@

\begin{quote}
    TBD: A library for reusable pieces of specification would be
    useful.
\begin{itemize}
    \item
        In section~\ref{sec:reusable-specs}, we showed how to reuse
        pieces of specification.
    \item
        It would be possible and useful to write a library that
        provides reusable pieces of specification, for many of
        Haskell's standard classes.
        (similar in purpose to
        {\tt
        checkers}\footnote{http://hackage.haskell.org/package/checkers})
\end{itemize}
\end{quote}

>>>>

\begin{quote}
    TBD: ``Section'' to ``section''
\end{quote}

@@

\begin{quote}
    TBD: introduce \emph{test driver}

    sol: not sure if it is necessary, @mkl, @kazu?
\end{quote}

@@

    sol: I think it is not critical.  I'll try to resolve this
    tomorrow, but I think we can always remove it.

@@

\begin{quote}
    TBD: state that ``A library for reusable pieces of specification would be
    useful.''
\begin{itemize}
    \item
        In section~\ref{sec:reusable-specs}, we showed how to reuse
        pieces of specification.
    \item
        It would be possible and useful to write a library that
        provides reusable pieces of specification, for many of
        Haskell's standard classes.
        (similar in purpose to
        {\tt
        checkers}\footnote{http://hackage.haskell.org/package/checkers})
\end{itemize}
\end{quote}
